### 2014-10-01 tex/proofs.tex
Added commentary

\subsection{Theorems}
\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rightarrow^*_S
(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
location mutual exclusive.
\end{lemma}
\begin{proof}
Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.

%\begin{comment}
%%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
%\begin{theorem}
%\label{thm:colex}
%If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
%$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
%\end{theorem}
%\begin{proof}
%The proof will proceed inductively.
%
%Base Case: In the initial state $s_0$ there is only one location, and all of it's fields are initialized to contain the uninitiated reference $\cfgnt{r}_{un}$. Since the only reference is the uninitialized reference, for which the desired property holds by construction, the property is true for all references on the heap.
%
%Inductive Step: 
%Suppose we have a summary state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_S s_s^\prime$. If all relevant fields are initialized, then $s_s = s_s^\prime$, and the property holds trivially. If there is some uninitialized fields, then on of those fields will have a new reference $\cfgnt{r}_{new}$ added to it. The disjunction
%$$ \bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r}_{new})\}$$
%Takes the form
%\begin{align*}
% (\phi_0) \vee (\neg \phi_0 \wedge \phi_1) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge \phi_2) \vee ...\\
% ... \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \phi_n) \vee (\neg \phi_0 \wedge \neg \phi_1 \wedge ... \wedge \neg \phi_n)
% \end{align*}
% Which reduces to $\cfgt{true}$. Thus, the collective exhaustion property holds for intermediate states. Because the property holds for intermediate states, for summary machine rules we will assume without loss of generality that all relevant fields are initialized. 
% Suppose that the rule executed in the transition from $s_s$ to $s_s^\prime$ is the field read rule. 
%Suppose we have a state $s_s$ for which the property holds, and some state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$. 
% 
%\end{proof}
%\end{comment}
%\begin{lemma}
%\label{lem:ref}
%For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
%\begin{equation}
%\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
%\end{equation}
%\end{lemma}
%\begin{proof}
%\end{proof}
%
%\begin{lemma}
%\label{lem:path}
%If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
%\end{lemma}
%\begin{proof}
%\end{proof}

@@

@@

\begin{theorem}
The representation relation $\sqsubset$ is a bisimulation.
\end{theorem}

>>>>

\subsection{Theorems}

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation as defined in
\eqref{eqn:BisimulationForwards} and
\eqref{eqn:BisimulationBackwards}. This proof is accomplished by
showing that the requisite homomorphism, $\rightharpoonup_h$, used in
the representation relation exists. A bisimulation is a relation over
pairs of states such that whenever two states, $s_\ell$ and
$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
s_\varsigma$, every successor, from either state, $s_\ell
\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
s_\varsigma^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.

If the $\varsigma$-relation is considered to be a model of the
$\ell-relation$ (i.e., a representation of that machine), then the
representation relation, as a bisimulation, ensures that the
$\varsigma$-relation is complete in that it any property that can be
shown in the $\ell$-relation can also be shown in the
$\varsigma$-relation; and further, the representation relation as a
bisimulation ensures that the $\varsigma$-relation is also sound in
that any property that can be shown to hold in the $\varsigma$-relation
can also be shown to hold in the $\ell$-relation.

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that each
rule preserves exactness. That is to say that whenever the state on
the left of the $\varsigma$-relation has a corresponding state that it
represents in the $\ell$-relation, its successor set is both sound and
complete relative the $\ell$-relation and subject to the
representation relation. Intuitively, the $\varsigma$-relation, at a
given state, has a successor to account for every successor from the
$\ell$-relation at the corresponding state, and the $ell$-machine has
a successor to account for every successor in the
$\varsigma$-relation.

The proof of exactness of each rule relies on the ability to derive
from the homomorphism in the representation relation in the current
state, a new homomorphism that is sufficient to use in the
representation relation that reasons over the successor states. The
proof is constructive in that it shows how given a valid homomorphism
for the current state, it is possible to derive a new homomorphism to
reason about successor states.

There are two slight complications in the proof: the field access rule
relies on the $S$-relation that operates on a different state that
then $\varsigma$-relation and constructing the new homomorphism in the
equals-reference rule relies on the incoming heap being location
mutual exclusive. The $S$-relation effectively produces an
intermediary state that is the state where uninitialized references
are initialized before the field access actually takes place. In
essence, a state on the left of the $\varsigma$-relation that is a
field access, undergoes a transition in which its heap is changed to
initialize fields. Once the fields are initialized, then the actual
field access takes place. The state with the heap that has the
initialized fields is the intermediary state between the state on the
left of the $\varsigma$-relation and the state on the right of the
$\varsigma$-relation. The proof reasons separately about this
intermediary state to prove that it too is exact.

The equals-reference proof must show that any given reference in the
heap is not able to point to two distinct locations at the same
time. If the incoming heap is able to point to two valid locations at
a given reference at the same time, then the help is
non-deterministic, and it is not possible to construct a valid
homomorphism from the existing homomorphism: which location should be
used in the map? As such, the proof first establishes that
$\varsigma$-relation preserves location mutual exclusive in the
incoming heap. Once that is shown, the exactness of the equals
reference rule is given.

The final statement that $\sqsubset$ is a bisimulation is in \thref{th:bisim}.

@@

\begin{lemma}[$\rightarrow^*_S$ preserves location mutual exclusion]
Given a location mutual exclusive heap, $(\cfgnt{L}_0\ \cfgnt{R}_0)$, from a
summary state with a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the
new heap, $(\cfgnt{L}^\prime\ \cfgnt{R}^\prime)$, from the summary
initialization machine, $(\cfgnt{L}_0\ \cfgnt{R}_0\ \cfgnt{r}\ \cfgnt{f})
\rightarrow^*_S
(\cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \cfgnt{r}\ \cfgnt{f})$, after any number of machine steps, is also
location mutual exclusive.
\end{lemma}
\begin{proof}
Induction over the number of machine steps on the summary initialization machine in \figref{fig:symInit}.

@@

\begin{theorem}
\label{th:bisim}
The representation relation $\sqsubset$ is a bisimulation.
\end{theorem}
